---
title: "R Project 1 - Hello R"
author: "Dung 'Ryan' Dang"
date: "1/23/2020"
output: 
  html_document: 
    fig_caption: yes
    fig_height: 10
    highlight: tango
    theme: yeti
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

the datasaurus_dozen file has 3 collums. The variables included are dataset,x,y.

### Exercise 2



First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=7, fig.width=7}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the star dataset:

```{r plot-star, fig.height=7, fig.width=7}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
### Exercise 4

First let's plot the data from the circle dataset:

```{r plot-circle, fig.height=7, fig.width=7}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between 'x' and 'y' in this data set
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)

Let's plot all the data from the dataset:

```{r}
  ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")
```
  
  
  Finally let's calculate the summary correlation coefficients:
  
  ```{r}
  datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
  ```
  